manuscript

### 2021-07-25 reports/manuscript.Rmd
updates manuscript review section

```{r diagnosis as a predictor all sessions}
temp_mixed_func <- function(varname){
  out <- df_rbans_long %>%
    filter(subtest == varname) %>%
    lmer(z_score ~ diagnosis + session + (1|rbansid), data = .)
  return(out)
}

@@

dims <- c("dim_celek", "dim_kratkodobapamet", "dim_dlouhodobapamet",
          "dim_pozornost", "dim_rec", "dim_vizuoprostor")
res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), "diagnosisschizophrenia")})
knitr::kable(as.data.frame(res),
             caption = "Diagnosis as a predictor of RBANS performance while controlling for the effect of participant and session.
             Coefficients are for schizophrenia in contrast to MDD (negative = schizophrenia does worse)")

>>>>

```{r diagnosis as a predictor all sessions}
temp_mixed_func <- function(varname){
  out <- df_rbans_long %>%
    filter(subtest == varname) %>%
    lmer(score ~ diagnosis*session + (1|rbansid), data = .)
  return(out)
}

@@

dims <- c("dim_celek", "dim_kratkodobapamet", "dim_dlouhodobapamet",
          "dim_pozornost", "dim_rec", "dim_vizuoprostor")
res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), "diagnosisschizophrenia:session")})
knitr::kable(as.data.frame(res),
             caption = "Interaction between diagnosis and session as a predictor of RBANS performance while controlling for the effect of participant and session. Coefficients are for schizophrenia in contrast to MDD (negative = schizophrenia does worse)")

res <- sapply(dims, function(x){report_mixed_effect(temp_mixed_func(x), "diagnosisschizophrenia")})
knitr::kable(as.data.frame(res),
             caption = "Diagnosis as a predictor of RBANS performance while controlling for the effect of participant and session. Coefficients are for schizophrenia in contrast to MDD (negative = schizophrenia does worse)")
